---
title: "Penguins"
subtitle: 'MSc in Statistics 2025/26, Imperial College London'
author: "Jai Robinson"
format:
  html:
    toc: true
    highlight: tango
    self-contained: true
    df-print: paged
  pdf: default
format-links: false
bibliography: "MSc_Statistics_coursework_template_quarto.bib" 
---

```{=html}
<style type="text/css">
h1{
  font-size: 24pt;
}
h2{
  font-size: 18pt;
}
body{
  font-size: 12pt;
}
</style>
```

```{r setup, include = FALSE, tidy=TRUE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
include_solutions <- TRUE
```

```{r setup2, include=FALSE, tidy=TRUE}
require(rmarkdown)
require(knitr)
require(kableExtra)
# Put any library imports and other preamble here.
```

# Plots

Initial look at time against weight

```{r, echo=FALSE}
plot(x= ChickWeight$Diet,
     y= ChickWeight$weight)
```
# Age vs weight

```{r}
#| echo: false
par(mfrow = c(2, 2))
for (i in unique(ChickWeight$Diet)){
    plot(
    x = ChickWeight[ChickWeight$Diet==i, "Time"],
    y = ChickWeight[ChickWeight$Diet==i, "weight"],
    col = i,
    pch = 15 + as.numeric(i),
    xlab = "Age (days)",
    ylab = "Weight",
    sub = paste("Diet: ", i)
  )
}
```



# Tables

How many chicks were on each diet?
@casella2024statistical
@rfcapital

```{r}

diet_counts <- table(ChickWeight$Diet)
knitr::kable(diet_counts, col.names = c("Diet", "Count"))

```
We will the mean and s.d. of each diet

```{r}



```



# Code appendix

Rather than re-paste all the code to the appendix, here is a trick which makes the markdown file output all the code (without) execution in the appendix, without any duplication.

Please keep in mind to format the code so that the entire code is clearly visible and does not run into the margins of the pdf version.

```{r ref.label=knitr::all_labels(), echo = T, eval = F}
```

# References
:::refs
:::

